DATA 624 Homework 10

### 2020-04-30 DATA624/HW10.Rmd
Finished HW 10

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA,
                      message = FALSE, warning = FALSE)
library(dplyr)
library(kableExtra)
library(tidyr)
library(igraph)
library(arules)
library(arulesViz)
knitr::knit_hooks$set(inline = function(x) {
  if (!is.numeric(x)) {
    x
  } else {
    prettyNum(round(x, 2), big.mark = ",")
  }
})
options(scipen = 999)

# Make sure to keep the default for normal processing.
default_output_hook <- knitr::knit_hooks$get("output")

# Output hooks handle normal R console output.
knitr::knit_hooks$set(output = function(x, options) {

  comment <- knitr::opts_current$get("comment")
  if (is.na(comment)) comment <- ""
  can_null <- grepl(paste0(comment, "\\s*\\[\\d?\\]"),
                     x, perl = TRUE)
  do_null <- isTRUE(knitr::opts_current$get("null_prefix"))
  if (can_null && do_null) {
    # By default R print output aligns at the right brace.
    align_index <- regexpr("\\]", x)[1] - 1
    # Two cases: start or newline
    re <- paste0("^.{", align_index, "}\\]")
    rep <- comment
    x <- gsub(re, rep,  x)
    re <- paste0("\\\n.{", align_index, "}\\]")
    rep <- paste0("\n", comment)
    x <- gsub(re, rep,  x)
  }

  default_output_hook(x, options)

})

knitr::opts_template$set("kill_prefix" = list(comment = NA, null_prefix = TRUE))
```

@@

```{r}
transactions <- read.transactions("GroceryDataSet.csv", sep=",")
```

```{r}
itemFrequencyPlot(transactions, topN=10, type="absolute", main="Top 10 Items")
```

In order to complete this market basket analysis, I will use the Apriori algorithm.

@@

If I am given the choice, I will use a network graph to preform the cluster analysis.

@@

edges <- temp %>%
  rename(to = value) %>%
  merge(temp) %>%
  rename(from = value) %>%
  filter(to != from) %>%
  select(-shoper_id)

G <- graph_from_data_frame(edges)
```

```{r}
newman_girvan_clusters <- cluster_edge_betweenness(G)
dendPlot(newman_girvan_clusters, mode="hclust")
```

```{r}
plot(newman_girvan_clusters, G) 
```

>>>>

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA,
                      message = FALSE, warning = FALSE)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(tidyr)
library(igraph)
library(arules)
library(stats)
```

@@

First I will read in the data and explore it a bit by looking at the top 10 items purchased

```{r}
transactions <- read.transactions("GroceryDataSet.csv", sep=",")
itemFrequencyPlot(transactions, topN=10, type="absolute", main="Top 10 Items")
```

Whole milk is the most frequently purchased item.

In order to complete this market basket analysis, I will use the Apriori algorithm. I will print out the top 10 rules with their support, confidence and lift.

@@

I am going to look for item groupings.  I will use a network graph to preform the cluster analysis.  First I will need to create a network graph from the transaction data.  The I will detect the communities in the graph using the Louvain algorthym.

@@

louvain_communities <- temp %>%
  rename(to = value, from = shoper_id) %>%
  graph_from_data_frame(directed = FALSE) %>%
  cluster_louvain() %>%
  communities()
```

Now that all customers and items are assigned to one of `r length(louvain_communities)` clusters I will summarize them by naming them the items and giving the count of the shopers in the cluster.

```{r}
items <- as.character(unique(temp$value))

cluster_df <- data.frame(name = c(NA), members = c(NA)) %>% na.omit()

for (i in 1:length(louvain_communities)){
  cluster_name <- paste0(i,": ")
  cluster_members <- 0
  for (member in louvain_communities[[i]]){
    if (member %in% items){
      cluster_name <- paste0(cluster_name, member, " + ")
    } else {
      cluster_members <- cluster_members + 1
    }
  }
  cluster_name <- substr(cluster_name,1,nchar(cluster_name)-3)
  cluster_df <- rbind(cluster_df, data.frame(name = cluster_name, members = cluster_members))
}

cluster_df %>%
  arrange(desc(members)) %>%
  kable() %>%
  kable_styling()
```
